%-------------------------
% CV in LaTeX
% Author: Yutong Zhang
% Credit: Aras Gungore
% License: MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\usepackage[margin=1.0in]{geometry}
\input{glyphtounicode}

\definecolor{link}{RGB}{56, 118, 191}
\hypersetup{
    colorlinks=true,
    linkcolor=link,
    urlcolor=link,
}

%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
% \addtolength{\oddsidemargin}{-0.5in}
% \addtolength{\evensidemargin}{-0.5in}
% \addtolength{\textwidth}{1.0in}
% \addtolength{\topmargin}{-0.5in}
% \addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
    \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
    \item\small{
        {#1 \vspace{-1.5pt}}
    }
}


\newcommand{\resumeSubheading}[4]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small #3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \textit{\small #1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeEducationHeading}[4]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & #2 \\
        \textit{\small #3} & \textit{\small #4}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeTutorHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{\small #1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        #1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeOrganizationHeading}[4]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{#2} \\
        \textit{\small #3} & \textit{\small #4}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-2pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-7pt}}

%---------- RESUME STARTS HERE ----------
\begin{document}

%---------- HEADING ----------

\begin{center}
    \textbf{\Huge Yutong Zhang} \\ \vspace{3pt}
    \small
    \faMobile \hspace{.5pt} \href{tel:18582149131}{+1 858 214 9131}
    $|$
    \faEnvelope \hspace{.5pt} \href{mailto:yuz049@ucsd.edu}{yuz049@ucsd.edu}
    $|$
    \faGraduationCap \hspace{.5pt} \href{https://scholar.google.com/citations?user=wuaUYbYAAAAJ&hI}{Google Scholar}
    $|$
    \faGithub \hspace{.5pt} \href{https://github.com/TonyZYT2000}{GitHub}
\end{center}



%----------- EDUCATION -----------

\section{Education}
    \vspace{3pt}
    \resumeSubHeadingListStart
        \resumeEducationHeading
            {University of California San Diego}
            {La Jolla, USA}
            {M.S. in Computer Science; \textbf{GPA: 4.00/4.00}}
            {Sep. 2022 \textbf{--} present}
        \resumeEducationHeading
            {University of California San Diego}
            {La Jolla, USA}
            {B.S. in Computer Science and Mathematics; \textbf{GPA: 3.95/4.00}}
            {Sep. 2018 \textbf{--} Jun. 2022}
    \resumeSubHeadingListEnd



%----------- RESEARCH INTEREST -----------
\section{Research Interest}
    \vspace{3pt}
    My current research interest centers around modeling complex dynamics with computational physics models.
    I have a broad interest in autonomous robot manipulation through optimization and an intense curiosity about integrating data-driven learning techniques for enhanced robustness.
    I want to explore using differentiable programming as an efficient tool for developing integrated robotic systems with percetpion, simulation and control.



%----------- RESEARCH EXPERIENCE -----------

\section{Research Experience}
    \vspace{3pt}
    \resumeSubHeadingListStart
        \resumeSubheading{Advanced Robotics and Contorls Lab}
        {La Jolla, USA}
        {Student Researcher, advised by Prof. Michael Yip}
        {Mar. 2021 \textbf{--} present}
        \resumeItemListStart
            \resumeItem{
                Developed visualization tools in C++ and OpenGL to visualize threads, ropes, and robot arms.
            }
            \resumeItem{
                Wrote modules to synchronize robot joint status from ROS topics to the visualization program.
            }
            \resumeItem{
                Created a differentiable position-based dynamics simulator for thin-shell, volumetric, and rope-like deformable objects in Python and PyTorch.
            }
            \resumeItem{
                Applied the differentiable simulator to autonoumous cloth manipulation. Formulated the task as a trajectory optimization problem constrained by safety thresholds to prevent undesired collision.
            }
            \resumeItem{
                Collaborated on the real-to-sim problem of modeling soft tissues in robot surgery. Utilized the differentiable simulator for online optimization of physical parameters to reduce the error.
            }
            \resumeItem{
                Currently parallelizing the simulator with the NVIDIA Warp library to accelerate the computation.
            }
        \resumeItemListEnd
    \resumeSubHeadingListEnd



%----------- PUBLICATIONS -----------

\section{Publications}
    $^\dagger$ equal contribution
    \vspace{-3pt}
    \resumeSubHeadingListStart
        \resumeSubItem{
            {[1]} Fei Liu, \textbf{Yutong Zhang}, Xiao Liang, and Michael Yip.
            Dynamic Coupling of Rigid and Deformable Objects for Geometrically Constrained Trajectory Optimization.\\
            \textit{IEEE Transactions on Robotics (T-Ro)}.\\
            \textit{\textbf{\textcolor{red}{In Preparation}}}\hspace{.5pt}
        }
        \resumeSubItem{
            {[2]} \textbf{Yutong Zhang}$^\dagger$, Fei Liu$^\dagger$, Xiao Liang, and Michael Yip.
            Achieving Autonomous Cloth Manipulation with Optimal Control via Differentiable Physics-Aware Regularization and Safety Constraints.\\
            \textit{IEEE International Conference on Robotics and Automation (ICRA), 2024}.\\
            \textit{\textbf{\textcolor{red}{Under Review}}}\hspace{.5pt}
            \href{https://arxiv.org/pdf/2309.11655.pdf}
            {\faFilePdfO \hspace{.5pt} [arXiv]},
            \href{https://www.youtube.com/watch?v=za2I0Kx4Co4}
            {\faYoutubePlay \hspace{.5pt} [video]}.
        }

        \resumeSubItem{
            {[3]} Fei Liu$^\dagger$, Xiao Liang$^\dagger$, \textbf{Yutong Zhang}, Yuelei Li, Shan Lin, and Michael C. Yip.
            Real-to-Sim Deformable Object Manipulation: Optimizing Physics Models with Residual Mappings for Robotic Surgery.\\
            \textit{IEEE International Conference on Robotics and Automation (ICRA), 2024}.\\
            \textit{\textbf{\textcolor{red}{Under Review}}}\hspace{.5pt}
            \href{https://arxiv.org/pdf/2309.11656.pdf}
            {\faFilePdfO \hspace{.5pt} [arXiv]}.
        }
    \resumeSubHeadingListEnd


%----------- PROJECTS -----------
\section{Projects}
    \vspace{2.5pt}
    \resumeSubHeadingListStart
        \resumeSubheading{Differentiable PBD Simulation}{}{Lead Developer}{}
        \resumeItemListStart
            \resumeItem{Developed an end-to-end differentiable position-based simulator for deformable objects in Python.}
            \resumeItem{Designed several trajectory optimization experiments for cloth manipulation with safety constraints.}
            \resumeItem{Embedded the simulation into the real-to-sim registration framework to optimize parameters online.}
            \resumeItem{Combining the framework with articulate body simualtion to uniformly solve robot dynamics.}
        \resumeItemListEnd
        \resumeSubheading{ARC Particle Sim}
        {\href{https://github.com/TonyZYT2000/WorkLog/blob/master/Yutong\%20Zhang.md}
        {\faFileText \hspace{.5pt} Report}}
        {Co-Developer}{}
        \resumeItemListStart
            \resumeItem{Developed a cross-platform visualization and simulation program in C++ and OpenGL.}
            \resumeItem{Visualized captured rope data in time sequence with second-order interpolation.}
            \resumeItem{Designed interactive GUI controls for visualization theme and playback frame rate.}
            \resumeItem{Implemented modules to synchronize joint angles from ROS topics to visualize the robot arm.}
        \resumeItemListEnd

        \resumeSubheading{The Meoze Runner}
        {\href{https://cse125.ucsd.edu/2022/cse125g4/blog/}
        {\faExternalLinkSquare \hspace{.5pt} Homepage},
        \href{https://github.com/ucsd-cse125-sp22/cse125-sp22-group4}
        {\faGithub \hspace{.5pt} Code}}
        {Graphics Developer}{}
        \resumeItemListStart
            \resumeItem{Developed a multiplayer 3D game in C++ and OpenGL with 6 teammates.}
            \resumeItem{Worked on graphics modules to manage mesh data and render with texture mapping.}
            \resumeItem{Implemented an efficient 2D oriented bounding box collision checking utility for the game server.}
            \resumeItem{Wrote Python scripts to export collision data from level designs done in Blender to the game server.}
        \resumeItemListEnd

        \resumeSubheading{Monte Carlo Path Tracer}
        {\href{https://tonyzyt2000.github.io/TonyZYT2000.github.io.archive/en/tags/CSE168/}
        {\faFileText \hspace{.5pt} Report}}
        {Developer}{}
        \resumeItemListStart
            \resumeItem{Developed a Monte Carlo Path Tracer in C++ and the NVIDIA OptiX framework.}
            \resumeItem{Wrote various BRDFs including Phong model, GGX microfacet model and Disney Principled BRDF.}
            \resumeItem{Implemented Russian Roulette techniques and multiple importance sampling to reduce noises.}
            \resumeItem{Extended an additional Photon Mapping pass to produce better caustics for transparent objects.}
        \resumeItemListEnd
    \resumeSubHeadingListEnd



%----------- TUTORING EXPERIENCE -----------

\section{Tutoring Experience}
    \vspace{3pt}
    \resumeSubHeadingListStart
        \resumeTutorHeading{UC San Diego, CSE 167 Computer Graphics}
        {Jan. 2022 \textbf{--} Mar. 2022}
        \resumeTutorHeading{UC San Diego, CSE 105 Theory of Computation}
        {Mar. 2021 \textbf{--} Jun. 2021}
    \resumeSubHeadingListEnd



%----------- SKILLS -----------

\section{Skills}
    \vspace{3pt}
    \resumeSubHeadingListStart
        \small{\item{
            \textbf{Programming Languages:}
            {\textit{\textbf{Experienced in}} C, C++, Python;
            \textit{\textbf{Familiar with}} MATLAB, Java, Scheme } \\
            \vspace{3pt}

            \textbf{Frameworks \& Libraries:}
            {CUDA, Eigen, OpenGL, ImGui, Warp, NumPy, SciPy, PyTorch, PyVista} \\
            \vspace{3pt}

            \textbf{Software Tools:}
            {Git, ROS, Bash, Linux, CMake, Docker, LaTeX, Blender, Houdini} \\
            \vspace{3pt}
        }}
    \resumeSubHeadingListEnd



%-------------------------------------------
\end{document}
